I am grateful to many outstanding professors and colleagues at the 
University of Illinois at Urbana-Champaign, as well as the national 
laboratories, who have supported and encouraged me. I want to express my 
sincere gratitude towards my advisor, Professor Kathryn Huff,
for her valuable support throughout this project. She offered perpetual 
encouragement, patience, and guidance without which I would not have been able 
to complete this thesis. 

I would also like to thank the professors who served in my committee: Tomasz 
Kozlowski, James Stubbins, and Luke Olson, not only for reviewing and 
assessing this work but also for the knowledge and guidance they offered. I 
am similarly grateful to my internship advisor, Dr. Benjamin Betzler from 
ORNL, for his technical and practical guidance. Finally, I would like to thank 
Professor Rizwan Uddin for his expert assessment of this work.

Special thanks to the NPRE faculty and staff, who have continuously aided and 
guided me since my very first day on campus. I would like to thank Becky 
Meline for her help in planning and managing my graduate study process. At the 
risk of neglecting someone, I thank Barbara, Hannah, Margaret, Grace, and 
Kristie for their help in processing my paperwork, arranging examinations, and 
this thesis format check. 

I would also like to thank my colleagues Jin Whan Bae, Alex Lindsay, Gavin 
Ridley, Gyu Tae Park, Greg Westphal, Sun Myung Park, Anshuman Chaube, 
Gwendolyn Chee, Roberto Fairhurst Agosta, Zoe Richer, Sam Dotson, and Mehmet 
Turkmen for their thoughts, valuable discussion, and help during my doctoral 
research and writing. I would like to recognize Matt Kozak for constructive 
criticism of the manuscript. 

This work would not be accomplished without limitless love and support of my 
wife, Nelli, and my daughters, Sofiya and Zoe. Their support in my dark days 
and patience in listening to my complaints are priceless. I have wholehearted 
thankfulness for my mother and my sisters, who have always encouraged me in 
all my beginnings and without whom this work would not have been possible. 
Above all, I am particularly indebted to my father, Igor Rykhlevskii. He 
passed away shortly after my doctoral studies began but was and always will be 
in my heart, inspiring me in all my endeavors.

This work was carried out in the Advanced Reactors and Fuel Cycles Group 
(ARFC) of the University of Illinois at Urbana-Champaign. This work was 
supported by the U.S. Department of Energy ARPA-E MEITNER Program (award 
DE-AR0000983). This research is part of the Blue Waters sustained-petascale 
computing project, which is supported by the National Science Foundation 
(awards OCI-0725070 and ACI-1238993) and the state of Illinois. Blue Waters is 
a joint effort of the University of Illinois at Urbana-Champaign and its 
National Center for Supercomputing Applications.